Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
paper: Replace underscores with XXX

The second dataset we used was Gigaword. This dataset is based on ____,
containing 110,382,986 tokens in the training set, 549,0454 tokens in the
validation set and ____ tokens in the test set. The combined dictionary
contains ____ unique tokens.

@@

____

>>>>

The second dataset we used was Gigaword. This dataset is based on XXX,
containing 110,382,986 tokens in the training set, 549,0454 tokens in the
validation set and XXX tokens in the test set. The combined dictionary
contains XXX unique tokens.

@@

XXX
